A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises

### 2018-05-07 paper.tex
Set up for citations

@@

\author{Andrew Wonnacott\\
  Advisers: Professor Dave Walker, Professor Matt Weinberg}

@@

\thispagestyle{empty}
\doublespacing{}
\begin{abstract}
  Student interest in ``Economics and Computing'', Princeton's undergraduate computer science course in algorithmic game theory, has grown rapidly in recent years.
  This course employs small simulations to develop students' ability to use theoretical tools to analyze more real-world situations.
  These strategy design exercises require considerably more software infrastructure than a usual theoretical problem set would, including handout code for student self-evaluation and software auto-graders.
  While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly-structured assignments and evaluating student submissions in the context of each other.
  In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary components of these strategy design assignments.
  Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
  This provides feedback from real student and instructor users, which was then used to improve the auto-grader design.
  Empirical results demonstrate the importance of quality tooling to effective use of instructor time, low broken submission rates, and high student satisfaction.
\end{abstract}

\newpage
\section*{Introduction}
My work builds upon existing programming-based game theory exercises assigned in Princeton's COS 445 ``Economics and Computing''.
The intention of these strategy design exercises is to teach students how to use game theory to analyze a real-world situation and work rationally within a healthy incentive structure, e.g.\ one in which students do not try to hurt each others’ performance.
Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{registrar data here}\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}

@@

\section*{Problem Background}
Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.\footnote{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
These programming-based exercises take a common form.

Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
A classic iterated game is the iterated prisoner's dilemma\footnote{Figure: PD game -> Java interface}, in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
Players balance the incentive to defect, which improves their own situation while damaging their opponent, with the knowledge that their opponent may defect in future rounds punish them if they defect now.
While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
These examples are not exhaustive, but illustrate the variety of course topics with potential for translation to iterated games.

@@

While the strategy design exercises assignments are popular with students\footnote{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused runtime exceptions, requiring considerable additional instructor resources.

\section*{Related Work}
This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.\footnote{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different abstract games: Prisoner's Dilemma, Centipede, and Ultimatum.
In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{an auction of multiple items, one after another, where the winning bid pays the second highest bid. This is the auction format used by Google to sell sponsored search auctions.}

Both problem sets were implemented and graded by Cyril Zhang\footnote{https://github.com/cyrilzhang}, a graduate student TA for the course.
Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
However, his implementation of software for strategy design assignments was intended for grader use only.
It is not modular and has to be completely rewritten for each assignment.
The student interfaces were documented, but the grader software was not documented for future use.
Additionally, some of the scripts and notebooks used by Zhang were not preserved and were not accessible as resources.
Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Zhang's code.

Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014\footnote{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
In both semesters, Yonatan Naamad,\footnote{https://github.com/ynaamad/} a former graduate student TA for the course, was responsible for software development.

The only resources available from Fall 2012 were collected from the course Google Code repository.\footnote{https://code.google.com/archive/p/cos445-scripts/}
This repository contains incomplete Python skeleton code for a basic tournament of an unspecified game.
I uploaded this code to the current course repository\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.

The Spring 2014 iteration of the course was developed on a private GitHub repository.\footnote{https://github.com/ynaamad/cos445}
Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
The Java code was the student handout, which contained strategy interfaces and some testing code.
The testing code was not designed to be automated for grading and was not modular.
It tested manually-entered strategies against each other, and assignment-specific details such as game structure and payoffs were integrated within the simulation code.
As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
These resources were uploaded to the current course repository,\footnote{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.

Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
However, a survey of several universities' courses, including courses at Harvard\footnote{https://beta.blogs.harvard.edu/k108875/}, Stanford\footnote{https://theory.stanford.edu/~tim/364a.html and https://theory.stanford.edu/~tim/f16/f16.html}, Cornell\footnote{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington\footnote{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale\footnote{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn\footnote{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech\footnote{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon\footnote{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke,\footnote{https://www2.cs.duke.edu/courses/spring16/compsci590.4/} identified only one other course with similarly-structured assignments.

Harvard's Computer Science 136, ``Economics and Computation'',\footnote{https://beta.blogs.harvard.edu/k108875/assignments/} assigns two programming problem sets.
The first requires implementation of a peer-to-peer file sharing system similar to Bittorrent, a protocol in which incentives parallel Prisoner's Dilemma.
However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
The second assignment is a strategy design exercise built on the generalized second-price auction, in which student strategies vary and are graded based on their performance in a competitive environment.
This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and the implementation is in Python.
While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445.

Many universities, including Princeton, maintain extensive systems for the automatic submission and processing of student assignments.
Such resources are useful in the general case of developing new programming-based assignments, but no such resources replicate the behavior implemented in this project.
Most auto-grading systems are designed with an assumption that each student submission is graded in isolation from other student submissions.
Such systems are not applicable to this project since the strategy design exercises involve evaluation of student strategy performance in a common environment.
Though existing automatic grading systems cannot replicate the full extent of this work, I have integrated existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
I integrated CS DropBox\footnote{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.

@@

Many students suggested the assignments be implemented in Python,\footnote{per survey 1 results} and this would be preferred by the course staff as well.
Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parameterized on user-input strategy names.
Unfortunately, COS 445's prerequisite courses only provide Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.\footnote{COS 333 survey data}
Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
These scripting languages were used only where Java would not suffice and only where implementation details were irrelevant to student assignment comprehension.

@@

However, several default Java behaviors do not map cleanly onto the desired properties of strategy design exercises.
For instance, Java objects used as function parameters are passed by mutable, nullable reference.
This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and nonnull unless otherwise explicitly specified.
Current industry standards for Java code obviate both of these issues using modern language features.\footnote{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}\footnote{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}\footnote{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
In order to preserve backwards compatibility, these features are not implemented by default.
Where possible, I have taken advantage of these features.
Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
However, I have not included \texttt{NotNull} annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.\footnote{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}

While of lesser urgency, I have also planned ahead to ensure the reusability of my work.
I elected to store this work in a University-owned private GitHub repository.
I also documented the repository structure and contents, including a summary of the process of developing and deploying a new assignment.
This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.

\section*{Implementation}
% TODO: signposting
% TODO: make it fit
Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
The game simulates college admissions using stable matchings.
While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.\footnote{Kernighan and Pike chapter 4}
I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.

@@

However, because of conscious design decisions to factor out repeated code from assignment implementations, my implementation has accomplished what previous implementations had not.
It is modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
It is reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
\footnote{TODO redraw using Powerpoint}
\footnote{TODO use this diagram when I talk about modularization earlier}
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
  \caption{TODO: This is a gray image.}\label{fig:gray}
\end{figure}

\subsection*{Handout Implementation}
In order to design my framework, I reviewed non-modularized code from the Spring 2017 auctions exercise.
This is the only assignment for which I had access to both the student handout and the grader code.
In any strategy design exercise, after the game design is complete, the next step is to implement is the student interface.
The interface for the auctions exercise is quite simple:\footnote{TODO:\ make this code a figure}
\begin{minted}{java}
import java.util.List;

@@

    // Let you know if you won, and how much the winners paid
    // Called once per day after the auction
    public void addResults(List<Double> bids, int myBid, double myPayment);
}
\end{minted}
This interface describes the necessary functions of a student strategy for the auctions execise.
Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results'') and assign different values to words auctioned on different days.
The strategy also has access the winning bids for each of the ten sponsored results from each past day and knows which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
These constants are not documented in the interface as designed, only in the assignment specification.
The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
Zhang also implemented a program used to grade the student-submitted strategies which consisted of two methods: \texttt{main} and \texttt{trial}.
The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
The latter contained an implementation of the generalized second-price auction format described in the assignment specification.

@@

During the development of this handout, however, the statically-typed nature of Java raised some difficulty.
Zhang's grader code had student submission names hardcoded into complex expressions, as though they had been copied in from a manually-written list formatted using \texttt{sed}.
In the context of developing a handout to allow students to test multiple strategies of their own design, I determined that requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
Additionally, graders desire functionality to configure the list of evaluated strategies without having to manually list out all the student strategy names and modify it to identify and diagnose misbehaving student strategies.
Since Java is not able to type-check user-input strategy names, I determined that the most effective workaround for this issue would be to automatically rewrite the Java code before compile-time.

For this purpose, I developed a simple Python script capable of rewriting arbitrary template plaintext files using a CSV file.
This script, \texttt{formatBase.py},\footnote{TODO: appendix this} builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
In its input, it identifies lines which start with \texttt{//R} and end with \texttt{//}.
For each such line in its input, it outputs multiple lines, each corresponding to the input line rewritten using a distinct row of the CSV by replacing each curly-enclosed key with the corresponding value.
It also rewrites the key \texttt{0} with the row number from the configuration table.
This script directly injects the contents of the configuration file into the Java code with no escaping, as is necessary in this application.
However, this practice is extremely dangerous, since using a user-submitted configuration file would allow users to execute arbitrary code on the evaluation machine.
Fortunately, this is not a security concern, since students already run arbitrary code on the evaluation machine: their submitted strategy.

>>>>

\usepackage{appendix}
\usepackage{titling}

@@

\author{
  Andrew Wonnacott\\
  Advisers: Professor Dave Walker, Professor Matt Weinberg
}

@@

\doublespacing{}

\begin{titlingpage}
  \begin{abstract}
    Student interest in ``Economics and Computing'', Princeton's undergraduate computer science course in algorithmic game theory, has grown rapidly in recent years.
    This course employs small simulations to develop students' ability to use theoretical tools to analyze more real-world situations.
    These strategy design exercises require considerably more software infrastructure than a usual theoretical problem set would, including handout code for student self-evaluation and software auto-graders.
    While some frameworks for automated grading exist, none surveyed provided the specific features desired for repeatedly developing very similarly-structured assignments and evaluating student submissions in the context of each other.
    In order to facilitate more automated grading of these assignments in this and future semesters, I have developed a framework of modular, extensible tools for building all of the necessary components of these strategy design assignments.
    Concurrently, in my role as a grader for COS 445, I used the framework to develop and evaluate four strategy design assignments, using assignment specifications developed with Professor Weinberg.
    This provides feedback from real student and instructor users, which was then used to improve the auto-grader design.
    Empirical results demonstrate the importance of quality tooling to effective use of instructor time, low broken submission rates, and high student satisfaction.
  \end{abstract}
\end{titlingpage}

\section*{Introduction}
My work builds upon existing programming-based game theory exercises assigned in Princeton's COS 445 ``Economics and Computing''.
The intention of these strategy design exercises is to teach students how to use game theory to analyze a real-world situation and work rationally within a healthy incentive structure, e.g.\ one in which students do not try to hurt each others’ performance.
Each past offering of the course has rebuilt these assignments, and all associated instructor tooling, from scratch, resulting in unnecessarily high allocation of instructor time to grading.
Additionally, the course has grown rapidly to become the single largest theoretical computer science course ever taught at Princeton.\footnote{More students complete COS 340 in a given year, but it is taught in both fall and spring semesters.}~\cite{coursesizes}

@@

\section*{Problem Background}
Four Princeton University departments offer courses in game theory: Economics, Politics, Mathematics, and Computer Science.
While all of these courses teach the core concepts of game theory, each also connects this core to relevant examples and topics in its department.
For instance, the Computer Science department's ``Economics and Computing'' places emphasis on the connections between game-theoretic results and algorithms, software, and other aspects of computer science.
The course focuses on the relevance of game theory to matchings, auctions, cryptocurrencies, and other multi-actor computational systems.~\cite{https://www.cs.princeton.edu/~smattw/Teaching/cos445sp18.htm}
It is also represented in the design of the problem sets, which, in addition to traditional proof-based exercises, contain programming-based exercises which connect course topics to prerequisite computer science skills.
These programming-based exercises take a common form.

Students are presented with an iterated game, described both in the assignment handout and as a Java interface.
A classic iterated game is the iterated prisoner's dilemma,\footnote{Figure: PD game -> Java interface} in which two players must collaborate to receive the best outcome and have access to the other player's previous decisions when making their own decision.
Players balance the incentive to defect, which improves their own situation while damaging their opponent, with the knowledge that their opponent may defect in future rounds punish them if they defect now.
While this game is well-studied and models some real-world incentive structures, the course also draws on various real-world phenomenon to design iterated games, including a college admissions game from the perspective of stable matchings, a search advertisement bidding game using auction theory, an election informed by voting theory, a gerrymandering-prevention simulation inspired by fair division, and exploitation of a fictional cryptocurrency by analyzing blockchain incentives.
These examples are not exhaustive, but illustrate the variety of course topics with potential for translation to iterated games.

@@

While the strategy design exercises assignments are popular with students~\cite{https://reg-captiva.princeton.edu/chart/index.php?terminfo=1184\&courseinfo=012095 requires CAS login}, they also demand dedication of considerable instructor resources to building software for student handouts and strategy evaluation, which have historically been significantly rebuilt for each assignment.
Worse still, due to course staffing changes, this work has not been preserved between semesters, resulting in inefficient allocation of department resources to producing new exercises without the institutional memory or software resources previously developed.
Due to the limited tooling provided in past semesters for students to test their code, many submissions did not compile or caused run-time exceptions, requiring considerable additional instructor resources.

\section*{Related Work}
This work was developed to replace previous software design exercises assigned to COS 445 students\footnote{including the author} in Spring 2017.~\cite{https://web.archive.org/web/20170916042726/https://www.cs.princeton.edu/~smattw/Teaching/cos445sp17.htm}
In one problem set, students developed and implemented strategies for three different strategy design exercises related to three different abstract games: Prisoner's Dilemma, Centipede, and Ultimatum.
In a later problem set, an exercise placed students in the role of bidders in a generalized second-price auction.\footnote{A G.S.P.\ auction is an auction of multiple items, one after another, where the winning bid pays the second highest bid. This is the auction format used by Google to sell sponsored search auctions.}

Both problem sets were implemented and graded by Cyril Zhang~\cite{https://github.com/cyrilzhang}, a graduate student TA for the course.
Zhang developed interfaces, dummy implementations, and grader software for each strategy design exercise.~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s17 requires invite: contact author or department}
However, his implementation of software for strategy design assignments was intended for grader use only.
It is not modular and has to be completely rewritten for each assignment.
The student interfaces were documented, but the grader software was not documented for future use.
Additionally, some of the scripts and notebooks used by Zhang were not preserved and were not accessible as resources.
Thus, while these resources served as inspiration for this work and provided some assignment-specific code to my work developing specific assignments, I did not build directly on Zhang's code.

Prior to Spring 2017, COS 445 was taught by Professor Mark Braverman in Fall 2012 and Spring 2014~\cite{https://precourser.io/course/1184012095 requires Princeton CAS authentication}.
Though no documentation or archives of the course homepage from these semesters is available online or in the Internet Archive, I recovered some resources from the course account on the ``Cycles'' cluster of the Princeton Computer Science department and from the source code repositories used by the course staff.
In both semesters, Yonatan Naamad,~\cite{https://github.com/ynaamad/} a former graduate student TA for the course, was responsible for software development.

The only resources available from Fall 2012 were collected from the course Google Code repository.~\cite{https://code.google.com/archive/p/cos445-scripts/}
This repository contains incomplete Python skeleton code for a basic tournament of an unspecified game.
I uploaded this code to the current course repository~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/f12 requires invite: contact author or department} but did not develop it further.

The Spring 2014 iteration of the course was developed on a private GitHub repository.~\cite{https://github.com/ynaamad/cos445}
Through a clone of this repository stored on Cycles, I discovered that the course had PHP and Java implementations of strategy design exercises for Prisoner's Dilemma and another auction setting.
The Java code was the student handout, which contained strategy interfaces and some testing code.
The testing code was not designed to be automated for grading and was not modular.
It tested manually-entered strategies against each other, and assignment-specific details such as game structure and payoffs were integrated within the simulation code.
As a design decision I dismissed the available PHP code, which was used for course grading, due to language unfamiliarity.
These resources were uploaded to the current course repository,~\cite{https://github.com/PrincetonUniversity/cos445-hw/tree/s14 requires invite: contact author or department} but were not reused, in part because they were located and examined only when I was given access to the course site in order to deploy my project.

Beyond COS 445 at Princeton, many universities have taught computer science courses in algorithmic game theory.
However, a survey of several universities' courses, including courses at Harvard~\cite{https://beta.blogs.harvard.edu/k108875/}, Stanford~\cite{https://theory.stanford.edu/~tim/364a.html}~\cite{https://theory.stanford.edu/~tim/f16/f16.html}, Cornell~\cite{https://www.cs.cornell.edu/courses/cs6840/2014sp/}, U.\ Washington~\cite{https://courses.cs.washington.edu/courses/cse522/05sp/}, Yale~\cite{https://zoo.cs.yale.edu/classes/cs455/fall11/}, U.\ Penn~\cite{https://www.cis.upenn.edu/~aaroth/courses/agtS15.html}, Georgia Tech~\cite{https://web.archive.org/web/20131002121909/https://www.cc.gatech.edu/\%7Eninamf/LGO10/index.html}, Carnegie Mellon~\cite{https://www.cs.cmu.edu/~arielpro/15896s16/index.html}, and Duke~\cite{https://www2.cs.duke.edu/courses/spring16/compsci590.4/}, identified only one other course with similarly-structured assignments.

Harvard's Computer Science 136, ``Economics and Computation''~\cite{https://beta.blogs.harvard.edu/k108875/assignments/}, assigns two programming problem sets.
The first requires implementation of a peer-to-peer file sharing system similar to BitTorrent, a protocol in which incentives parallel Prisoner's Dilemma.
However, the assignment is not a competition and student solutions are not differentiated based on strategic properties.
The second assignment is a strategy design exercise built on the generalized second-price auction, in which student strategies vary and are graded based on their performance in a competitive environment.
This is very similar to both the Spring 2014 and Spring 2017 auction exercises of COS 445 at Princeton.
However, the grading structure of this assignment is quite different from the grading structure of the COS 445 strategy design exercises, and the implementation is in Python.
While comparison between COS 445 assignments and CS 136 assignments in a future project might provide some pedagogical value, such work would be out of scope for this project.
Given that these assignments are implemented in Python, only handout (and not grading) code is available, and the assignments are graded differently, these resources were dismissed as a base for development of new resources for COS 445.

Many universities, including Princeton, maintain extensive systems for the automatic submission and processing of student assignments.
Such resources are useful in the general case of developing new programming-based assignments, but no such resources replicate the behavior implemented in this project.
Most auto-grading systems are designed with an assumption that each student submission is graded in isolation from other student submissions.
Such systems are not applicable to this project since the strategy design exercises involve evaluation of student strategy performance in a common environment.
Though existing automatic grading systems cannot replicate the full extent of this work, I have integrated existing resources for assignment submission and student feedback to perform smaller tasks within a larger system.
I integrated CS DropBox~\cite{https://csguide.cs.princeton.edu/academic/csdropbox} functionality where relevant, and I modeled the leaderboard structure after review of the leaderboard implementation used in other Princeton CS classes.
Generally, no such tools would leverage the high degree of structural similarity between strategy design exercises, and a dedicated project for these exercises will allow for more efficient development and evaluation.

@@

Many students suggested the assignments be implemented in Python,~\cite{per survey 1 results} and this would be preferred by the course staff as well.
Members of the Mechanism Design group are not expected to have working proficiency with Java, but many have enough experience with Python to support students.
Additionally, Python's conciseness and ability to load classes from user input would be useful when implementing tools which are parameterized on user-input strategy names.
Unfortunately, COS 445's prerequisite courses only provide Java experience, and not Python experience, so students reasonably expect they will only be asked to write Java code.
Data from other course surveys indicate that 90\% of students report themselves fluent in Java after the Princeton introductory sequence, compared to 30\% for Python, confirming that the student work for the assignment must be in Java.~\cite{COS 333 survey data}
Given this constraint, and lacking any other language selection pressures, I elected to implement as much of the assignment code as possible in Java, with limited usage of scripting languages such as Python, Bash, and GNU Make.
These scripting languages were used only where Java would not suffice and only where implementation details were irrelevant to student assignment comprehension.

@@

However, several default Java behaviors do not map cleanly onto the desired properties of strategy design exercises.
For instance, Java objects used as function parameters are passed by mutable, nullable reference.
This is in contrast to functional languages (including Ocaml and Rust), where parameters are immutable and non-null unless otherwise explicitly specified.
Current industry standards for Java code obviate both of these issues using modern language features.~\cite{https://github.com/google/guava/wiki/UsingAndAvoidingNullExplained}~\cite{https://github.com/google/guava/wiki/ImmutableCollectionsExplained}~\cite{https://docs.oracle.com/javase/7/docs/api/java/util/Collections.html\#unmodifiableList(java.util.List)}
In order to preserve backwards compatibility, these features are not implemented by default.
Where possible, I have taken advantage of these features.
Since the assignment specification documents that students are required not to modify parameters, instructor code can use unmodifiable (immutable) containers.
However, I have not included \texttt{NotNull} annotations because they are not taught in the prerequisite courses and, as previously noted, these assignments should not require students to self-teach any programming skills.
In my own framework code, which must be supported by future instructors, I decided to assume support for Java 9, released in fall 2016, and to use modern language features, since course instructors are at least as likely to have industry experience with modern Java code as experience with the Princeton introductory sequence.~\cite{https://www.techworld.com/news/developers/java-9-release-date-new-features-3660988/}

While of lesser urgency, I have also planned ahead to ensure the re-usability of my work.
I elected to store this work in a University-owned private GitHub repository.
I also documented the repository structure and contents, including a summary of the process of developing and deploying a new assignment.
This ensures that future course staff will have the physical and technical means to maintain this project after I have graduated.

\section*{Implementation}
% TODO: signposting
% TODO: make it fit
Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
The game simulates college admissions using stable matchings.
While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.~\cite{Kernighan and Pike chapter 4}
I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.

@@

However, because of conscious design decisions to factor out repeated code from assignment implementations, my implementation has accomplished what previous implementations had not.
It is modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
It is reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
% TODO redraw using Powerpoint
% TODO use this diagram when I talk about modularization earlier
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
  \caption{TODO: This is a gray image.}\label{fig:gray}
\end{figure}

\subsection*{Handout Implementation}
In order to design my framework, I reviewed non-modular code from the Spring 2017 auctions exercise.
This is the only assignment for which I had access to both the student handout and the grader code.
In any strategy design exercise, after the game design is complete, the next step is to implement is the student interface.
The interface for the auctions exercise is quite simple, as shown in Figure~\ref{minted:Bidder}.
\begin{figure}[hbt]
\begin{minted}{java}
import java.util.List;

@@

    // Let you know if you won, and how much the winners paid
    // Called once per day after the auction
    public void addResults(List<Double> bids, int myBid, double myPayment);
}
\end{minted}
  \caption{\texttt{interface Bidder} demonstrates a strategy interface}\label{minted:Bidder}
\end{figure}
This interface describes the necessary functions of a student strategy for the auctions exercise.
Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results'') and assign different values to words auctioned on different days.
The strategy also has access the winning bids for each of the ten sponsored results from each past day and knows which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
These constants are not documented in the interface as designed, only in the assignment specification.
The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
Zhang also implemented a program used to grade the student-submitted strategies which consisted of two methods: \texttt{main} and \texttt{trial}.
The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
The latter contained an implementation of the generalized second-price auction format described in the assignment specification.

@@

During the development of this handout, however, the statically-typed nature of Java raised some difficulty.
Zhang's grader code had student submission names hard-coded into complex expressions, as though they had been copied in from a manually-written list formatted using \texttt{sed}.
In the context of developing a handout to allow students to test multiple strategies of their own design, I determined that requiring students to modify the simulator Java code whenever they changed which strategies they wanted to test would be so cumbersome that the simulator might not have been distributed at all.
Additionally, graders desire functionality to configure the list of evaluated strategies without having to manually list out all the student strategy names and modify it to identify and diagnose misbehaving student strategies.
Since Java is not able to type-check user-input strategy names, I determined that the most effective workaround for this issue would be to automatically rewrite the Java code before compile-time.

For this purpose, I developed a simple Python script capable of rewriting arbitrary template plain-text files using a CSV file.
This script, \texttt{formatBase.py}, included as Appendix~\ref{appendix:formatBase}, builds a list of dictionaries, one for each row of the CSV, using the header of the CSV as the keys and the contents of the row as the values.
In its input, it identifies lines which start with \texttt{//R} and end with \texttt{//}.
For each such line in its input, it outputs multiple lines, each corresponding to the input line rewritten using a distinct row of the CSV by replacing each curly-enclosed key with the corresponding value.
It also rewrites the key \texttt{0} with the row number from the configuration table.
This script directly injects the contents of the configuration file into the Java code with no escaping, as is necessary in this application.
However, this practice is extremely dangerous, since using a user-submitted configuration file would allow users to execute arbitrary code on the evaluation machine.
Fortunately, this is not a security concern, since students already run arbitrary code on the evaluation machine: their submitted strategy.

Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thereby rewritten to instantiate one implementation of each Student class listed in the configuration file:
\begin{figure}[hbt]
\begin{minted}{java}
    // S, T, W are simulation parameters documented in the student interface
    public static int[] oneEachTrial(double S, double T, double W)
    {
        // Initialize students
        Student[] students = new Student[N];
        //R students[{0}] = new Student_{netID}();//
        return runTrial(students, S, T, W);
    }
\end{minted}
  \caption{\texttt{oneEachTrial} demonstrates usage of \texttt{formatBase.py}}\label{minted:oneEachTrial}
\end{figure}

My modular design allows for data collection code to vary without additional overhead.
The following method instantiates an instance of an instructor-provided strategy using reflection, in addition to the strategies specified in the configuration file.
This method is useful for grading assignments.
\begin{figure}[hbt]
\begin{minted}{java}
    public static <Student_T extends Student> int[] withExtraTrial(
            Class<Student_T> clazz, double S, double T, double W)
    {
        // Initialize students
        Student[] students = new Student[N+1];
        //R students[{0}] = new Student_{netID}();//
        try {
            students[N] = clazz.getConstructor().newInstance();
        } catch (ReflectiveOperationException roe) {
            roe.printStackTrace();
            System.exit(1);
        }

        return runTrial(students, S, T, W);
    }
\end{minted}
  \caption{\texttt{withExtraTrial} demonstrates modularity in data processing}\label{minted:withExtraTrial}
\end{figure}
